\texttt{davos}: The Python package smuggler

### 2022-04-07 paper/main.tex
use hyphenat package to allow linebreaks in \texttt
finished problems section

\usepackage[colorlinks=true, urlcolor=blue, pdfborder={0 0 0}]{hyperref}
\usepackage{breakurl}

@@

Second, typical environment management tools don't enforce that a particular requirements \textit{remain} satisfied after they are initially installed. While this provides a degree of flexibility in certain use cases, it makes it easy to inadvertently alter the set of installed Python packages after this initial setup. For example, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis requiring ``Package \textit{Y}." If Package \textit{Y} depends on version 1.1 of Package \textit{X}, then Package \textit{X} will be upgraded to accommodate this new requirement, potentially leading to inconsistent behavior of code that uses Package \textit{X} if this change goes unnoticed.

>>>>

\usepackage[colorlinks=true, urlcolor=blue, pdfborder={0 0 0}]{hyperref}
\usepackage{breakurl}
\usepackage[htt]{hyphenat}

@@

%Second, typical environment management tools don't enforce that specified requirements \textit{remain} satisfied after they are initially installed. This makes it easy to inadvertently alter existing packages in a Python environment at any point in time, potentially affecting the behavior of code that depends on them. For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}." If Package \textit{Y} depends on version 1.1 of Package \textit{X}, then Package \textit{X} will be upgrade to accommodate this new requirement. potentially altering or breaking the previous analyses  in future runs, as well as for anyone with whom  analysis code. Further, if earlier analyses require functionality

Second, although many tools exist for installing Python packages in an isolated environment from a fixed set of required packages (e.g., in a \texttt{requirements.txt}, \texttt{pyproject.toml}, \texttt{environment.yml}, \texttt{Pipfile}, \texttt{Dockerfile RUN} instruction, etc.), few if any enforce that the specified requirements \textit{remain} satisfied after this initial setup. The ability to modify an environment after its creation is useful in many cases (e.g., to install additional software as needed); however, it also makes it easy to inadvertently alter existing packages, potentially leading to subtle issues with code that relies on them. For instance, suppose a researcher has implemented a series of analyses using version 1.0 of ``Package \textit{X}," and decides to  perform an additional analysis that requires installing ``Package \textit{Y}." If Package \textit{Y} depends on version 0.9 of Package \textit{X}, then Package \textit{X} will be downgraded to accommodate this new requirement, potentially altering or breaking prior analyses for both the researcher and anyone with whom their code may be shared. Further, if certain analyses require Package \textit{Y} while others rely on a feature of Package \textit{X} not implemented until version 1.0, it's unclear which version the researcher should install in the environment.
